\section{Project Plan}
\subsection{System overview}
In this project, we aim to develop a visualized toolkit for
crowd-sourcing NLP annotations. The target audience are normal people
with little knowledge and patience. The toolkit would allow them to
quickly label NLP datasets.

There are two key properties of our toolkit: firstly, annotators could
interact with the data to understand them in a refresh way. Annotators
label some examples and they expect immediate feedback from the
toolkit. These feedbacks will help them understand the problem.
Secondly, the toolkit should enable and encourage trial and errors. It
would not assume any edits from the users as gold, but treat the edits
as clues to better visualize the data to the annotator. When the
annotator finishes a labeling task, he should be satisfied and
confident with the overall outcome. For example, it is hard to
distinguish whether ``Jeff" is ``Jeff Bilmes" or ``Jeffery Heer" when
data points are seen individually. But if the toolkit could immediate
show a big cluster $\{$``Jeff, Jeff Bilmes, Jeffery Heer, Professor
Heer"$\}$ after incorrectly merge two points, the annotators would
have a good chance to fix it.

In this project, we would focus on two important kinds of NLP
annotations: building trees (\eg\  parsing) and clustering (\eg\
coreference resolution). But we would keep in mind that the toolkit
should be easily extensible to any NLP problems. 
\subsection{Milestones}

\emph{System Brainstorming}
\\All group members work on this together.
\\[1\baselineskip]
\emph{System Input Output Implementation:}\\Major Responsibility: Congle Zhang \\Minor Responsibility: Shengliang Xu, Haichen Shen
\\[1\baselineskip]
\emph{System Graphic \& Visualization Implementation:} \\Major Responsibility: Haichen Shen， Shengliang Xu \\Minor Responsibility: Hanchuan Li, Congle Zhang 
\\[1\baselineskip]
\emph{System Layout Adjustment \& User Evaluation Study:} \\Major Responsibility: Hanchuan Li \\ Minor Responsibility: Congle Zhang, Haichen Shen, Shehgliang Xu.